The hydra and the rooster

### 2020-07-19 latex/chapter-ordinals.tex
simplification of class OrdinalNotation

@@

%%%% ICI %%%%%

@@

Let us consider how these notions are represented in \coq{}.

We can also associate to every ordinal $\alpha$ a set whose elements are all ordinals strictly less than $\alpha$. Thus, it is meaningful  to consider \emph{finite}, \emph{infinite}, \emph{demunerable} and \emph{non-countable} ordinals.
The relation $<$ on ordinals is well-founded, and the order $\leq$ associated with
$<$ is total.

Let us cite the book by Schütte~\cite{schutte} which contains an axiomatic definition of the set of countable ordinals we used as a mathematical specification of our implementation in \coq{}~\cite{CantorContrib}.

Out of respect of the tradition, the meta-variables for ordinals will be 
 $\alpha$, $\beta$, $\gamma$, etc.

>>>>

% ICI

\begin{todo}
Present instances of Ordinal notation.  
\end{todo}

@@

@@
